Metrics

### 2023-11-17 manuscript/manuscript.tex
Working on data preprocess

\title[Automatic Cause of Death Assignment from Narratives using ChatGPT: A Case Study of 11,000 Verbal Autopsies in Sierra Leone from 2019-2022]{Automatic Cause of Death Assignment from Narratives using ChatGPT: A Case Study of 11,000 Verbal Autopsies in Sierra Leone from 2019-2022}

>>>>

\title[Automatic Cause of Death Assignment from Narratives with ChatGPT: A Case Study of 11,000 Verbal Autopsies in Sierra Leone from 2019-2022]{Automatic Cause of Death Assignment from Narratives with ChatGPT: A Case Study of 11,000 Verbal Autopsies in Sierra Leone from 2019-2022}

### 2023-11-17 src/metrics.Rmd
Working on data preprocess

@@

    # Calc N if not known
    N <- if (is.null(N)) length(unique(c(actual, pred))) else N

@@

calc_csmf_acc <- function(actual, pred, causes = NULL) {

@@

>>>>

```{r, echo=FALSE}
knitr::opts_chunk$set(
  message=FALSE,
  warning=FALSE
)
```

## Libraries

```{r}
library(tidyverse)

options(readr.show_col_types = FALSE)
```

## Functions

Functions for PCCC and CSMF Accuracy.

@@

    # Calc N num of causes if not known
    N <- if (is.null(N)) length(unique(c(actual, pred))) else N

@@

calc_csmf_acc <- function(actual, pred) {

@@

## Data

Load data from `data` and `tmp` folders.

```{r}
df <- list(
    wva2016_icd10 = read_csv(
        "../data/wva2016_icd10_v1.csv",
        col_types = cols(wva2016_code = col_double())
    ),
    icd10_cghr10 = read_csv("../data/icd10_cghr10_v1.csv"),
    adult = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_adult_v1.csv",
            col_select = "rowid"
        ) %>% mutate(round = 1, age = "adult"),
        read_csv(
            "../tmp/healsl_rd2_adult_v1.csv",
            col_select = "rowid"
        ) %>% mutate(round = 2, age = "adult"),
    ),
    child = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_child_v1.csv",
            col_select = "rowid"
        ) %>% mutate(round = 1, age = "child"),
        read_csv(
            "../tmp/healsl_rd2_child_v1.csv",
            col_select = "rowid"
        ) %>% mutate(round = 2, age = "child")
    ),
    neo = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_neo_v1.csv",
            col_select = "rowid"
        ) %>% mutate(round = 1, age = "neo"),
        read_csv(
            "../tmp/healsl_rd2_neo_v1.csv",
            col_select = "rowid"
        ) %>% mutate(round = 2, age = "neo")
    ),
    model_chatgpt3 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        )
    ),
    model_chatgpt4 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        )
    ),
    model_insilicova = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_insilicova_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_insilicova_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        )
    ),
    model_interva5 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_interva5_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_interva5_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        )
    )
)
```

```{r, echo=FALSE}
for (i in names(df)) {
    print(i)
    print(head(df[[i]]))
}
```

## Preprocess

Convert ICD-10 and WVA-2016 codes to CGHR-10 codes.

```{r}

# Combine all models
models <- df[str_starts(names(df), "model_")]

# Add age groups to predictions
df$chatgpt3 <- df$chatgpt3 %>%
    left_join(
        df$adult,
        by = c(
            "rowid" = "rowid",
            "round" = "round"
        ),
        multiple = "first"
    )

# Convert wva2016 to icd10 via join
df$insilicova <- df$insilicova %>%
    left_join(
        df$wva2016_icd10,
        by = c("cause1_wva" = "wva2016_code"),
        multiple = "first"
    )
df$interva5 <- df$interva5 %>%
    left_join(
        df$wva2016_icd10,
        by = c("cause1_wva" = "wva2016_code"),
        multiple = "first"
    )

# Convert icd10 to cghr10 via join
df$chatgpt3 <- df$chatgpt3 %>%
    left_join(
        df$icd10_cghr10,
        by = c("api_chat_icd" = "icd10_code"),
        multiple = "first"
    )
df$interva5 <- df$interva5 %>%
    left_join(
        df$wva2016_icd10,
        by = c("cause1_wva" = "wva2016_code"),
        multiple = "first"
    )
```
